### 2019-10-26 ms/ms.tex
Complete draft

\documentclass[12pt]{report}
\usepackage[utf8]{inputenc}
\usepackage{times}
\renewcommand\thesection{\arabic{section}}
\usepackage[parfill]{parskip}
\usepackage{subcaption}
\usepackage{graphicx}
\usepackage[left=0.75in,right=0.75in,top=0.75in,bottom=0.75in]{geometry}
\usepackage{multirow}
\usepackage{hhline}
\usepackage{nth}
\usepackage{bm}
\usepackage{siunitx}
\usepackage[labelfont=bf]{caption}
\usepackage[doublespacing]{setspace}
\usepackage{filecontents}
\usepackage{lineno} \linenumbers
\usepackage{amsmath}

@@

We currently lack robust estimates of how species are shifting their
distributions in response to recent warming. The velocity of
temperature change---the rate a species would have to shift its range
to maintain constant temperature---has been calculated at 0.42 km/yr
\supercite{Loarie2009}. A meta-analysis of taxonomic groupsestimated
the average pole-ward shift in species' distributions has been
estimated as approximately 1.69 km/yr-1 \supercite{Chen2011},
suggesting that species might be capable of keeping pace with shifting
climate. Yet this estimate is derived from just a handful of studies,
and does not address the large variation in response among species.
Here we leverage the vast volume of distributional data stored in
digital data repositories\supercite{url_gbif} to provide the first
global synthesis of species distributional responses to climate
change. By contrasting historical niche dimensions with those of the
present day, we can characterise the true biotic velocity of climate
change, which represents the actual velocity with which species track
climate across space.

We show that, on average, species' historical (pre-1970) ranges have
warmed significantly, and that species have generally shifted their
distributions to ameliorate this warming. Yet this general pattern
masks a remarkably degree of variability in species responses: many
species' ranges are now even warmer than if their distibutions had
remained static. Further, we find that, while species' distributions
are strongly predicted by their evolutionary history and functional
traits, the same is not true of their degree of tracking. Thus while
species' static distributions are reasonably predictable, their
changes in distributions are not.

@@

Our approach has two main innovations: its focus on (1) the whole of a
species' distribution and(2) expected change. (1) We suggest that
something of a disconnect is developing among related fields of
ecology: species' range modelers typically focus on species'
limits\supercite{Sexton2009} (\emph{i.e.}, the upper and lower
quantiles) while community ecologists \supercite{Tilman2004} and
macro-evolutionary \supercite{Zanne2018} biologists focus on central
tendencies (\emph{i.e.}, the median). We therefore see no strong
\emph{a priori} reason that species can, or must, track all quantiles
equally, and so our approach is to check all quantiles of a species'
distribution. (2) The denominator of our index re-scales species'
change around an expectation under distributional stasis. We suggest
that species' changes should be measured on the basis of the magnitude
of change to which they are exposed. This change reflects the
magnitude of ecological and evolutionary selection, and while we
suggest there are many ways of addressing this, we suggest ours is the
simplest and so perhaps a fair starting point. We note that our index
could by re-scaling according to the distance that would need to be
travelled to match the degree of change (\emph{sensu}
\citeauthor{Loarie2009}\supercite{Loarie2009}), but prefer to present
here a dimensionless (and so unitless) index of tracking.
% ...something like this? I re-wrote everything to be about the
% "relative velocity of change" (which would have given us some fancy
% notation if we wanted it) but as we don't use distances or speeds I
% feel we ought not to?

@@

\textbf{Idiosyncratic drivers of species' tracking.} To examine the
potential drivers of species' ranges and range tracking, we first
examined the phylogenetic signal of species' climate quantiles. We
focused on mammals\supercite{xxx}, birds\supercite{xxx},
amphibians\supercite{xxx}, reptiles\supercite{xxx}, and
plants\supercite{xxx}, since we were able to find broadly inclusive,
dated phylogenies for these taxa. We found statistically significant
evidence of phylogenetic signal across XXX of 135
taxon-climate-quantile combinations of species' past ranges (and XXX
in the present; see figure \ref{phylogeny}). This is consistent with
the known patterns of phylogenetic conservatism outlined above. For
our index, however, we found evidence of phylogenetic signal in only
XXX combinations (XXXlist themXXX). This confirms the known results
that species' present-day and past ranges are strongly influenced by
evolutionary, but suggests that the magnitude of change (relative to
expectations) may be driven by different drivers.

We additionally examined species' traits as potential drivers of
species' distributions and potential to track changing environment. We
focused on mammals\supercite{xxx}, birds\supercite{xxx}, and
plants\supercite{xxx}, since global, openly-released trait datasets
exist for these taxa. Again, we found statistically significant
associations between traits and past distributions of XXX of XXX
taxon-climate-quantile combinations (XXX in the present; see figure
\ref{traits}). While the traits we used are strongly associated with
species' climate responses\supercite{xxx} (hence their strong
predictive power of species' distributions, but not tracking index),
we emphasize that we do not examine traits related to dispersal
ability. This is due to a paucity of open-access dispersal traits
\supercite{xxx}, and we highlight that future work should address
whether our index is explained by such drivers.
% Another potential problem here is no trait*env interaction, which I
% sense is also important...
% WILL - re-do TEMP.INDEX ~ TEMP! THERMOPHILES!!!

@@

If true, this result would explain the lack of association between
species' traits and evolutionary history with their degree of climate
tracking. The ecological and evolutionary rules that determine
species' climate relationships are changing, and thus the factors that
once are strong predictors of past and present distributions are not
predictive of the differences between them. Yet there are alternative
explanations, of which we highlight three: (1) that we have missed
fundamentally important environmental axes, (2) biotic interactions,
and (3) that our index highlights random variation in
distribution. (1) We fully acknowledge that we ignore potentially
relevant environmental drivers such as geology (and so soil), habitat,
and all Anthropogenic factors other than climate. We are not alone in
this simplification\supercite{xxx}, but we detect strong evolutionary
pattern in the factors we do examine in the data underlying our
index. (2) Competition and facilitation among species are likely
strong drivers of species' ability to track climate\supercite{xxx}. We
acknowledge it is entirely possible that ignoring these factors is the
driver of our result and, if so, we urge for an acceleration of the
inclusion of such information into broad-scale analyses
\supercite{xxx}. (3) If species were perfectly tracking climate
(\emph{i.e.}, $present_\tau$ is equal to $past_\tau$ in the absence of
sampling error or some other stochastic process) then our index values
would essentially be random numbers. There are good empirical evidence
that this is not the case \supercite{xxx} but, as we show in the
supplementary materials, simulations suggest out values are
incompatible with this result.

@@

\clearpage
% Figures

\begin{figure}[h!]
  \begin{center}
    \includegraphics[width=0.7\textwidth]{../figures/violin-tmp-50.pdf}
  \end{center}
  \caption{\doublespacing \textbf{Empirical distributions of track
      index for \nth{50} of mean temperature.} Need to add simulations
    to plot. Add phylo-pics?}
  \label{violin}
\end{figure}

\begin{figure}[h!]
  \begin{center}
    \includegraphics[width=0.7\textwidth]{../figures/pca-50.pdf}
  \end{center}
  \caption{\doublespacing \textbf{Principal components analyses of
      present and past climate, along with our index of climate
      tracking.} Loadings are correlated (eigenvalues shown at bottom
    of plot), but much weaker overall in index.}
  \label{pca}
\end{figure}

\begin{figure}[h!]
  \begin{center}
    \includegraphics[width=0.7\textwidth]{../figures/phylo-tmp-50.pdf}
  \end{center}
  \caption{\doublespacing \textbf{Phylogeny with ancestral states
      branches of past temperature (50th quantile) and tips of the
      temperature 50th index.} Scale between the two kinds of input
    data currently is slightly off, hence no scale bar, and obviously
    the tip colours are hideous, but I think no one would disagree
    there's signal in the underlying data!}
  \label{pca}
\end{figure}

% zoom in on one clade and show that the tips are a random subset (but the branches are not)
% Will wonders if we can put the correlation matrix to the side of an upward-facing tree
% have lines going outward from the tree to show mapping

\begin{figure}[h!]
  \begin{center}
  \end{center}
  \caption{\doublespacing \textbf{Trait correlation box.}
    XXXmissingXXX}
  \label{traits}
\end{figure}

@@

\textbf{Acknowledgments} WDP was funded by NSF ABI-1759965, NSF
EF-1802605, and USDA Forest Service agreement 18-CS-11046000-041. TJD
was funded by \emph{Fonds de Recherche Nature et Technologies} grant
number 168004.

@@

\section*{\Large Methods}

>>>>

\documentclass[12pt]{report}
\usepackage[utf8]{inputenc}
\usepackage{times}
\renewcommand\thesection{\arabic{section}}
\usepackage[parfill]{parskip}
\usepackage{subcaption}
\usepackage{graphicx}
\usepackage[left=0.75in,right=0.75in,top=0.75in,bottom=0.75in]{geometry}
\usepackage{multirow}
\usepackage{hhline}
\usepackage{nth}
\usepackage{bm}
\usepackage{siunitx}
\usepackage[labelfont=bf]{caption}
\usepackage[doublespacing]{setspace}
\usepackage{filecontents}
\usepackage{lineno} \linenumbers
\usepackage{amsmath}
\usepackage{pdflscape}

@@

We currently lack robust estimates of how species are shifting their
distributions in response to recent warming. The velocity of
temperature change---the rate a species would have to shift its range
to maintain constant temperature---has been calculated at 0.42 km/yr
\supercite{Loarie2009}. A meta-analysis of taxonomic groups estimated
the average pole-ward shift in species' distributions has been
estimated as approximately 1.69 km/yr-1 \supercite{Chen2011},
suggesting that species might be capable of keeping pace with shifting
climate. Yet this estimate is derived from just a handful of studies,
and does not address the large variation in response among species.
Here we leverage the vast volume of distributional data stored in
digital data repositories\supercite{url_gbif} to provide the first
global synthesis of species distributional responses to climate
change. By contrasting historical niche dimensions with those of the
present day, we can characterise the true biotic velocity of climate
change, which represents the actual velocity with which species track
climate across space.

We show that, on average, species' historical (pre-1970) ranges have
warmed significantly, and that species have generally shifted their
distributions to ameliorate this warming. Yet this general pattern
masks a remarkably degree of variability in species responses: many
species' ranges are now even warmer than if their distributions had
remained static. Further, we find that, while species' distributions
are strongly predicted by their evolutionary history and functional
traits, the same is not true of their degree of tracking. Thus while
species' static distributions are reasonably predictable, their
changes in distributions are not.

@@

Our approach has two main innovations: its focus on (1) the whole of a
species' distribution and(2) expected change. (1) We suggest that
something of a disconnect is developing among related fields of
ecology: species' range modellers typically focus on species'
limits\supercite{Sexton2009} (\emph{i.e.}, the upper and lower
quantiles) while community ecologists \supercite{Tilman2004} and
macro-evolutionary \supercite{Zanne2018} biologists focus on central
tendencies (\emph{i.e.}, the median). We therefore see no strong
\emph{a priori} reason that species can, or must, track all quantiles
equally, and so our approach is to check all quantiles of a species'
distribution. (2) The denominator of our index re-scales species'
change around an expectation under distributional stasis. We suggest
that species' changes should be measured on the basis of the magnitude
of change to which they are exposed. This change reflects the
magnitude of ecological and evolutionary selection, and while we
suggest there are many ways of addressing this, we suggest ours is the
simplest and so perhaps a fair starting point. We note that our index
could by re-scaling according to the distance that would need to be
travelled to match the degree of change (\emph{sensu}
\citeauthor{Loarie2009}\supercite{Loarie2009}), but prefer to present
here a dimensionless (and so unit-less) index of tracking.
% ...something like this? I re-wrote everything to be about the
% "relative velocity of change" (which would have given us some fancy
% notation if we wanted it) but as we don't use distances or speeds I
% feel we ought not to?

@@

\textbf{Idiosyncratic drivers of species' tracking.} To examine the
potential drivers of species' ranges and range tracking, we first
examined the phylogenetic signal of species' climate quantiles. We
focused on mammals\supercite{Faurby2015}, birds\supercite{Jetz2012},
amphibians \supercite{Jetz2018}, reptiles \supercite{Zheng2016}, and
plants\supercite{Smith2018}, since we were able to find broadly
inclusive, dated phylogenies for these taxa. We found statistically
significant evidence of phylogenetic signal across 158 of 180
taxon-climate-quantile combinations of species' past ranges (and 153
in the present; see figure \ref{phylogeny}). This is consistent with
the known patterns of phylogenetic conservatism outlined above. For
our index, however, we found evidence of phylogenetic signal in only
29 combinations. This confirms the known results that species'
present-day and past ranges are strongly influenced by evolutionary,
but suggests that the magnitude of change (relative to expectations)
may be driven by different drivers.
% Will: this is based on lambda *values* and so you need to update
% this with p-values...

We additionally examined species' traits as potential drivers of
species' distributions and potential to track changing environment. We
focused on mammals\supercite{Jones2009a,Wilman2014},
birds\supercite{Wilman2014}, and plants\supercite{Wright2004}, since
global, openly-released trait datasets exist for these taxa. Again, we
found statistically significant associations between traits and past
distributions of 193 of 240 taxon-climate-quantile combinations (203
in the present at $\alpha_{5\%}$; see figure \ref{traits}), but not
for between the traits and our tracking index (9 out of 240l
4\%). While the traits we used are strongly associated with species'
climate responses\supercite{Wright2004} (hence their strong predictive
power of species' distributions, but not tracking index), we emphasise
that we do not examine traits related to dispersal ability. This is
due to a paucity of open-access dispersal traits
\supercite{Gallagher2019}, and we highlight that future work should
address whether our index is explained by such drivers.
% Another potential problem here is no trait*env interaction, which I
% sense is also important...
% WILL - re-do TEMP.INDEX ~ TEMP! THERMOPHILES!!!

@@

If true, this result would explain the lack of association between
species' traits and evolutionary history with their degree of climate
tracking. The ecological and evolutionary rules that determine
species' climate relationships are changing, and thus the factors that
once are strong predictors of past and present distributions are not
predictive of the differences between them. A likely

Yet there are alternative
explanations, of which we highlight three: (1) that we have missed
fundamentally important environmental axes, (2) biotic interactions,
and (3) that our index highlights random variation in
distribution. (1) We fully acknowledge that we ignore potentially
relevant environmental drivers such as geology (and so soil), habitat,
and all Anthropogenic factors other than climate. We are not alone in
this simplification\supercite{xxx}, but we detect strong evolutionary
pattern in the factors we do examine in the data underlying our
index. (2) Competition and facilitation among species are likely
strong drivers of species' ability to track climate\supercite{xxx}. We
acknowledge it is entirely possible that ignoring these factors is the
driver of our result and, if so, we urge for an acceleration of the
inclusion of such information into broad-scale analyses
\supercite{xxx}. (3) If species were perfectly tracking climate
(\emph{i.e.}, $present_\tau$ is equal to $past_\tau$ in the absence of
sampling error or some other stochastic process) then our index values
would essentially be random numbers. There are good empirical evidence
that this is not the case \supercite{xxx} but, as we show in the
supplementary materials, simulations suggest out values are
incompatible with this result.

@@

\clearpage
% Figures
\clearpage
\begin{figure}[h!]
  \begin{center}
    \includegraphics[width=\textwidth]{../figures/violin-tmp-0-5.pdf}
  \end{center}
  \caption{\doublespacing \textbf{Most species are tracking global
      temperature, but there is pronounced variation among species and
      clades.} The vertical axis shows the \nth{50} quantile of our
    tracking index of annual mean temperature (boostrapped to account
    for variation in sampling; see methods). On the left, our seven
    major taxonomic groups plotted with the median and \nth{25} and
    \nth{50} quantiles of their distributions highlighted. At the
    far-right of the plot, output from our simulations of species that
    are moving but either imperfectly tracking, or not tracking at
    all, are shown. In the main text, we highlight that the majority
    of species are tracking global climate, but there is profound
    variation among species and clades. Fungi, insects, and reptiles
    are, broadly, tracking the \nth{50} quantile of mean temperature
    well, while other taxa (\emph{e.g.}, mammals and plants) are not.}
  \label{violin}
\end{figure}

\clearpage
\begin{landscape}
\begin{figure}[h!]
  \begin{center}
    \includegraphics[width=1.4\textwidth]{../figures/phylo-tmp-50.pdf}
  \end{center}
  \caption{\doublespacing \textbf{Despite strong phylogenetic signal
      in species' static distributions, species' changes in
      distributions are not phylogenetically patterned.} This is a
    single sample from the posterior distribution of plant phylogenies
    used for our analysis\supercite{Smith2018}. The two oldest
    branches have been shortened for clarity of presentation
    (emphasised with dashed lines). Its internal branches are
    ancestral state reconstructions, assuming Brownian motion, of
    species' median mean-temperature in the past. Its tips are
    coloured according to the track index of the same underlying data
    (compare with figure \ref{violin}). Both are coloured according to
    the legend at the bottom of the figure. While this is but a single
    plot (see also figure \ref{correls} and the supplementary
    materials), this general pattern of strong phylogenetic signal of
    climate, but not of degree of tracking, is true of almost all of
    our underlying data (see main text).}
  \label{pca}
\end{figure}
\end{landscape}

\clearpage
\begin{figure}[h!]
  \begin{center}
    \begin{subfigure}{.45\textwidth}
      \includegraphics[width=\textwidth]{../figures/traits-50.pdf}
      \caption{Trait correlations}
    \end{subfigure}
    \begin{subfigure}{.45\textwidth}
      \includegraphics[width=\textwidth]{../figures/physig-5.pdf}
      \caption{Phylogenetic signal}
    \end{subfigure}
  \end{center}
  \caption{\doublespacing \textbf{Species' static climate variables
      show strong trait correlations and phylogenetic signal, but
      their relative degree of tracking does not.} In (a), we show the
    correlation between the median of each climate variable (rows)
    with each of our traits (columns); colours are given at the right
    of the figure. In each cell, the outer, larger box depicts the
    correlation between species' present-day climate and the trait,
    while the smaller, inner box the correlation for species' relative
    tracking (whose size is proportional to intensity of
    correlation). The 3 (of 54) track-index correlations that are
    statistically significant (at $\alpha_{5\%}$) are highlighted with
    crosses. In (b), we show the phylogenetic signal (Pagel's
    $\lambda$\supercite{Pagel1999}) of the median of each taxonomic
    group's (columns) median species' climate variables and relative
    tracking indices (rows). As with (a), in each cell the outer,
    larger box depicts the correlation between species' present-day
    climate and the trait, while the smaller, inner box the
    correlation for species' relative tracking (whose size is
    proportional to phylogenetic signal strength). The single
    track-index metric for which phylogenetic signal was stronger than
    the underlying data is highlighted with a cross.}
  \label{traits}
\end{figure}

\clearpage
\begin{figure}[h!]
  \begin{center}
    \includegraphics[width=\textwidth]{../figures/pca-50.pdf}
  \end{center}
  \caption{\doublespacing \textbf{Species' movement through climate
      space differs from their current positions within it.} Each of
    our figures is a principal component analysis (PCA) biplots; in
    (a) of species' median past climate values, in (b) median present
    climate, and in (c) the median track-index of all climate
    variables. A PCA biplot shows correlations among the underlying
    data, with each axis explaining some amount of variation in the
    underlying data (labelled on the axes themselves). In (a) and (b),
    species' climate variables are correlated with one-another, and
    the space reflects global patterns in climate. In (c), this
    pattern has broken down: while some associations among climate
    axes still remain (notably temperature), the general pattern is
    one of independent shift through climate space.}
  \label{pca}
\end{figure}

@@

\textbf{Acknowledgements} WDP was funded by NSF ABI-1759965, NSF
EF-1802605, and USDA Forest Service agreement 18-CS-11046000-041. TJD
was funded by \emph{Fonds de Recherche Nature et Technologies} grant
number 168004.

@@

\section*{\Large Methods}
\section*{\Large Methods}
\renewcommand{\figurename}{Extended Data Figure}
\renewcommand{\tablename}{Extended Data Table}

All analyses were conducted in \texttt{R} version \texttt{3.6.1}
\autocite{R2018}. Code to reproduce all analyses in their entirety is
available in the online supplementary materials.

\subsection*{Data collation}

\textbf{Occurrence data.} Species' distribution data were downloaded
from the Global Biodiversity Information Facility (GBIF)
\supercite{url_gbif,url_gbif_occurrences}. We downloaded only data
highlighted by GBIF as not having any spatial issues, meaning they
contained no obvious location errors (\emph{e.g.}, latitude/longitude
swaps, coordinates that are rounded and so imprecise). These occurrence
data include records that were flagged as having potential issues and
then were corrected; in the supplementary materials, we show that
excluding these records leads to qualitatively identical results. We
present, in the main text, results from `human observation'
occurrences (\emph{e.g.}, human surveys); in the supplementary
materials observations based upon vouchered specimens (\emph{e.g.},
pressed specimens in a herbarium) whose results are qualitatively
identical. We worked only with occurrences from 1955--1980 and
1990-2015 (see also `metric calculation' below). We only worked with
species that had at least 1000 records on GBIF. This pragmatic
threshold limits us to better-studied species, but in preliminary
investigations we found our results to be robust to this threshold.

\textbf{Climate data.} Climate data were downloaded from
\citeauthor{Harris2014}\supercite{Harris2014}'s nine global
time-series. We split the data into yearly (averaged) $0.5^\circ$
cells, from which we estimated each of our nine climate variables for
each species observation.

\textbf{Trait and phylogenetic data.} Plant trait data were taken from
\citeauthor{Wright2004}\supercite{Wright2004} (leaf lifespan, leaf
mass-per-unit-area, leaf Nitrogen mass, and leaf photosynthetic
capacity), mammal body mass data from PanTHERIA\supercite{Jones2009a}
and EltonTraits \supercite{Wilman2014}, and bird body mass data from
EltonTraits \supercite{Wilman2014}. We were unable to find sufficient
coverage of the other taxa in this study in open-access trait
databases to facilitate further analysis. We used existing global
mammal\supercite{Faurby2015}, bird\supercite{Jetz2012}, amphibian
\supercite{Jetz2018}, and plant\supercite{Smith2018} phylogenies,
which contain posterior distributions of possible phylogenies which we
used to account for uncertainty (see `Trait and phylogenetic analyses'
below). For reptiles, we used
\citeauthor{Zheng2016}\supercite{Zheng2016}, which is a single
phylogeny and so we could not account for uncertainty with it in this
way. We were unable to find dated, global phylogenies for the other
taxa in this study.

\textbf{Taxonomic cleaning.}  We only made use of data for which
species identity was known, and we ignored variation among
sub-species. Species' taxonomy has changed through time, and so is a
potential source of bias in our analysis. As such, we used the World
Conservation Union's species taxonomy, through
\emph{taxize}\supercite{Chamberlain2013}, to harmonise all taxonomic
information. In cases where a species' name could not be found on the
IUCN, we retained that species in our analysis (since GBIF itself
performs taxonomic cleaning and standardisation).

\subsection*{Calculating and testing our track index}

\textbf{Bootstrapping procedure to account for sampling bias and
  empirical calculation of track index values.}  The sampling of
species through time and across space is known to be uneven across the
data in GBIF \supercite{Beck2013,Beck2014}. To ensure our method was
statistically robust to such changes, we employed a bootstrap
procedure during the calculation of $track_\tau$. To do this we
randomly re-sampled, with replacement, the occurrences making up
$present_\tau$ and $projected_\tau$ to be of the same number as
$past_\tau$, and vice-versa for $past_\tau$ and $present_\tau$. We
repeated this process 999 times, and report the median of the
bootstrapped distribution of $track_\tau$ here in the main text. We
applied this procedure to the occurrence data described above.

\textbf{Estimating the track index in simulated data.} To assess the
performance of our (bootstrapped) track index, we simulated species'
whose ranges tracked climate to varying extents through time. Full
results of the results of these simulations are given in the
supplementary materials, and a selection of simulations are shown i
figure \ref{violin}. Using the climate data from above in the years
1962 and 2002 (the mid-points of the ranges of our data), we simulated
species with varying maximum possible range sizes (1x1, 2x2, 5x5,
10x10, 20x20, or 50x50 grid-cell extents) and varying possible
latitudinal shifts in range ($\pm$1, 2, 5, or 10 grid-cells). We also
varied two other parameters: a species' degree of environmental
tracking ($\alpha$; taking a value of 0, 0.1, 0.2, ..., 0.9, or 1) and
overall fraction of chance occupancy ($\sigma$; taking a value of 0,
0.1, 0.2, ..., 0.9, or 1). Together, these two parameters define a
species' probability of being present within a cell within its
potential range:
$(1-\alpha) \times sigma + \alpha \times \mathcal{N}$.  $\mathcal{N}$
is defined as a scaled Normal probability density function with a mean
equal to the median of the species' distribution in 1962 and a
variance of 1. Thus a species with an $\alpha$ of 1 is present only in
cells within its range that resemble its climatic centre, and a
species with an $\alpha$ of 0 is present in proportion $\sigma$ of the
cells within its potential range. We simulated all possible
combinations of parameters 20 times, providing a full range of
potential range shifts.
% This needs more work!

\subsection*{Trait and phylogenetic analyses}

We calculated the Pearson's correlation between all estimated climatic
niche variables ($present_\tau$, $past_\tau$, $projected_\tau$,
$track_\tau$ and the bootstrapped $track_\tau$). While we show only a
handful of these correlations in figure \ref{traits}, we provide all
correlations in the supplementary figures (and note that the
qualitative results of all correlations are the same). For the
phylogenetic signal analyses, we likewise calculated Pagel's $\lambda$
(using \emph{phytools}\supercite{Revell2012phytools}) for all indices,
reporting all results in full in the supplementary materials (which
are again qualitatively identical to the results in the main text).
